---
title: "bootRasterCombine"
author: "Alex M. Chubaty and Isolde Lane-Shaw"
date: "15 March 2021"
output: 
  html_document: 
    keep_md: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, results = "hold")
```

```{r packages}
library("Require")
Require(c("PredictiveEcology/reproducible@development",
          "PredictiveEcology/SpaDES.core@development"))
Require("PredictiveEcology/LandR@development", require = FALSE)
```

# Overview

Provide an overview of what the module does / how to use the module.

Module documentation should be written so that others can use your module.
This is a template for module documentation, and should be changed to reflect your module.

# Usage

```{r module_usage, eval = FALSE}
scratchDir <- checkPath("~/scratch/bootRasterCombine", create = TRUE)

raster::rasterOptions(default = TRUE)
options(
  rasterMaxMemory = 5e+12,
  rasterTmpDir = scratchDir,
  reproducible.cacheSaveFormat = "qs"
)

setPaths(
  cachePath = checkPath("cache"),
  modulePath = file.path(".."),
  inputPath = "data",
  outputPath = "outputs"
)

times <- list(start = 0, end = 1)

cl <- parallel::makeCluster(parallel::detectCores() / 2)
parameters <- list(
  bootRasterCombine = list(
    cl = cl,
    scratchDir = scratchDir,
    .useCache = FALSE, ## TODO: use cache later
    .useFuture = TRUE,
    .verbose = TRUE
  )
)
modules <- list("bootRasterCombine")
objects <- list()
inputs <- list()
outputs <- list()

mySimOut <- simInitAndSpades(times = times, params = parameters, modules = modules, objects = objects)

parallel::stopCluster(cl)
```

# Parameters

Provide a summary of user-visible parameters.

```{r moduleParams, echo = FALSE, eval = TRUE}
df_params <- SpaDES.core::moduleParams("bootRasterCombine", "..")
knitr::kable(df_params)
```

# Events

Describe what happens for each event type.

## Init

Fetches the complete list of raw bootstrap raster files from Google Drive, saving a copy to disk.
Subsequent runs on the same machine will use this local stashed copy, so no additional downloads are needed.
If the Google Drive folder contents are updated, simply delete the `gdrive_ls_cache.qs` file in the module's data directory, and rerun the module to fetch the updated list.

## Download

Downloads all the raw bootstrap raster files from the Google Drive location.
*WARNING: total uncompressed size of all these files is ~330 GB.*

## Calculate mean and variance

Calculated per species across all BCRs.

## Mosaic

Mosaic all mean/var rasters across BCRs per bird species into a single `rasterLayer`.

## Upload

Upload the resulting mosaicked rasters to Google Drive.

# Data dependencies

## Input data

How to obtain input data, and a description of the data required by the module.
If `sourceURL` is specified, `downloadData("bootRasterCombine", "..")` may be sufficient.

```{r moduleInputs, echo = FALSE, eval = TRUE}
df_inputs <- SpaDES.core::moduleInputs("bootRasterCombine", "..")
knitr::kable(df_inputs)
```

## Output data

Description of the module outputs.

```{r moduleOutputs, echo = FALSE, eval = TRUE}
df_outputs <- SpaDES.core::moduleOutputs("bootRasterCombine", "..")
knitr::kable(df_outputs)
```

# Links to other modules

This module prepares data layers for use with BAM posthoc binning module (<https://github.com/ilaneshaw/postHocBinning>).
