---
title: "bootRasterCombine"
author: "Alex M. Chubaty and Isolde Lane-Shaw"
date: "10 March 2021"
output: html_document
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = "hold")
```

# Overview

Provide an overview of what the module does / how to use the module.

Module documentation should be written so that others can use your module.
This is a template for module documentation, and should be changed to reflect your module.

# Usage

```{r module_usage}
library("Require")
Require("SpaDES.core")

setPaths(modulePath = file.path(".."))
getPaths() # shows where the relevant paths are

times <- list(start = 0, end = 1)

parameters <- list(
  #.progress = list(type = "text", interval = 1), # for a progress bar
  ## If there are further modules, each can have its own set of parameters:
  #module1 = list(param1 = value1, param2 = value2),
  #module2 = list(param1 = value1, param2 = value2)
)
modules <- list("bootRasterCombine")
objects <- list()
inputs <- list()
outputs <- list()

mySim <- simInit(times = times, params = parameters, modules = modules, objects = objects)
mySimOut <- spades(mySim)
```

# Parameters

Provide a summary of user-visible parameters.

```{r moduleParams, echo = FALSE}
df_params <- moduleParams("bootRasterCombine", "..")
knitr::kable(df_params)
```

# Events

Describe what happens for each event type.

## Plotting

Write what is plotted.

## Saving

Write what is saved.

# Data dependencies

## Input data

How to obtain input data, and a description of the data required by the module.
If `sourceURL` is specified, `downloadData("bootRasterCombine", "..")` may be sufficient.

```{r moduleInputs, echo = FALSE}
df_inputs <- moduleInputs("bootRasterCombine", "..")
knitr::kable(df_inputs)
```

## Output data

Description of the module outputs.

```{r moduleOutputs, echo = FALSE}
df_outputs <- moduleOutputs("bootRasterCombine", "..")
knitr::kable(df_outputs)
```

# Links to other modules

This module prepares data layers for use with BAM posthoc binning module.

# TODO

- overview of what each of these pieces is trying to achieve and why they are being done in a certain way
    - describe the raw data (rasters), including file sizes, number of files, extents, general format etc.
    - where is GDAL being used? can we process these in memory?
    - can we parallelize? (if no, why not?)
    - what is the final desired 'output'? what species are needed?
- because only needs to be run once, cache cache cache!
- cropping/masking the rasters in postprocess before `calc()` because apparently some rasters of the same BCR and bird have different extents
- deletion of `folderRawBoot` contents periodically, or is there a way of just loading the rasters straight from google drive without actually downloading them?
    - why would you want to do this? this forces you to redownload files each time.
- extra `lapply` so multiple bird species can be given in bird list at once
- something saying what to do if a BCR or bird sp doesn't exist.
- what is with this error message that pops up sometimes but not other times??? Error in curl::curl_fetch_disk(url, x$path, handle = handle) : 
  OpenSSL SSL_read: Connection reset by peer, errno 104

